A Proposal for the Use of Backtranslation to Decode Whale Songs

### 2024-07-01 tex/paper.tex
Update tex file bib
fixing bib again
testing workflow
more testing CI integration

\section{Introduction}
Decoding whale songs presents a unique challenge in the field of animal communication. In this paper, we propose an unsupervised translation approach motivated by understanding animal communication. This involves using backtranslation techniques to create a model that can translate whale vocalizations into English and back, ensuring that the translations are contextually and semantically accurate.\\ \\
I will use the term "Whale" to refer to the language Whales are speaking. i.e., "She understands both Whale and English."

@@

\end{thebibliography}
\bibliographystyle{plain}
\bibliography{references}

\end{document}

>>>>

\section{Introduction}
Decoding whale songs presents a unique challenge in the field of animal communication. In this paper, I propose an unsupervised translation approach motivated by understanding animal communication. This involves using backtranslation techniques to create a model that can translate whale vocalizations into English and back, ensuring that the translations are contextually and semantically accurate.\\ \\
I will use the term "Whale" to refer to the language Whales are speaking. For example, "she understands both Whale and English."

@@

\end{thebibliography}
\end{document}
